\begin{thebibliography}{119}
\bibitem{Netflix} Netflix [Электронный ресурс]. --- Режим доступа: https://www.netflix.com/
\bibitem{youtube} YouTube [Электронный ресурс]. --- Режим доступа: https://www.youtube.com/
\bibitem{number-of-researches-2014} Beel, J. Research Paper Recommender System Evaluation: A Quantitative Literature
Survey [Текст] / J. Beel, B. Gipp, S. Langer [и др.] // International Journal on Digital
Libraries. 2015. С. 1---34
\bibitem{most-researched} Asanov, D. Algorithms and Methods in Recommender Systems [Текст] / D. Asanov // Berlin Institute
of Technology
\bibitem{rs-in-compsciense} Jannach, D. Recommender Systems in Computer Science and Information Systems --- A
Landscape of Research [Текст] / D. Jannach, M. Zanker, M. Ge [и др.] // International
Conference on Electronic Commerce and Web Technologies. 2012. С. 76---87.
\bibitem{cfrs} Ekstrand, M. D. Collaborative Filtering Recommender
Systems [Текст] / M. D. Ekstrand, J. T. Riedl, J. A. Konstan
// Foundations and Trends in Human-Computer Interaction. 2011. 3. Т. 4.  С. 81---173.
\bibitem{usenet} Konstan J. A. GroupLens: applying collaborative filtering to Usenet news [Текст] / J. A. Konstan,
B. N. Miller, D. Maltz [и др.] // Communications of the ACM. 1997. Т. 40.
С. 77---87.
\bibitem{item-based} Sarwar, B. Item-based collaborative filtering recommendation algorithms [Текст] / B. Sarwar,
G. Karypis, J. Konstan [и др.] // Proceedings of the 10th international conference
on World Wide Web. 2001. С. 285---295.
\bibitem{framework-cf} Herloker, J. L. An algorithmic framework for performing collaborative filtering [Текст]  / J. L. Herlocker,
J. A. Konstan, A. Borchers [и др.] // Proc. of SIGIR. 1999.
\bibitem{e-commerce} Sarwar, B. Analysis of recommendation algorithms for e-commerce [Текст]  / B. Sarwar, G. Karypis,
J. Konstan [и др.] // In Proceedings of ACM E-Commerce. 2000. С. 158---167.
\bibitem{content8}. Herlocker, J.L. Content-Independent Task
Recommendation [Текст]  / J. L. Herlocker, J. A. Konstan // IEEE Internet Computing. Т. 5. С. 40---47.
Focused
\bibitem{cf-expert} Herlocker, J. L. Explaining collaborative filtering
recommendations / J. L. Herlocker, J. A. Konstan, J. Rield
// Proceedings of the 2000 ACM conference on Computer
supported cooperative work. 2000. С. 241---250

\bibitem{heur3} Berkovsky, S. Cross-Domain Mediation in Collaborative [Текст] 
Filtering / S. Berkovsky, T. Kuflik, F. Ricci
// Proceedings of the 11th international conference on User Modeling.
2007. С. 355---359
\bibitem{rs-handbook} Ricci, F. Recommender Systems Handbook [Текст]  / F. Ricci, L. Rokach, B. Shapira [и др.] // New
York, NY, USA: Cambridge University Press, 2011
\bibitem{heur1} Tuzhilin, A. Improving Collaborative Filtering Recommendations
Using External Data [Текст]  / A. Umyarov, A. Tuzhilin // ICDM ’08 Proceedings of the 2008 Eighth IEEE
International Conference on Data Mining. 2008. С. 618---627
\bibitem{toward} Adomavicius, G. Toward the Next Generation of Recommender
Systems: A Survey of the State-of-the-Art and Possible Extensions [Текст]  / G. Adomavicius, A. Tuzhilin// IEEE
Transactions on Knowledge and Data Engineering. 2005. С. 734---749
\bibitem{2d} Adomavicius, G. Context-Aware Recommender Systems Using
collaborative filtering to weave an information [Текст]  / G. Adomavicius, A. Tuzhilin. // Recommender Systems
Handbook. 2011. С. 217---253
\bibitem{topn1} Karypis, G. Evaluation of item-based top-N recommendation algorithms [Текст]  / G. Karypis //
Proceedings of the International Conference on Information and Knowledge
Management. 2001. с. 247---254
\bibitem{topn2} Karypis, G. Item-based top-N recommendation algorithms [Текст]  / M. Deshpande, G. Karypis// ACM
Transactions on Information Systems. 2004. С. 143---177
\bibitem{cluster1} Herlocker, J. L. Clustering items for collaborative filtering [Текст]  / J. L. Herlocker // Proceedings of
the ACM SIGIR Workshop on Recommender Systems (SIGIR ’99). 1999
\bibitem{heur2} Wang, J. Unifying user-based and item-based collaborative filtering approaches
by similarity fusion [Текст]  / J. Wang // SIGIR ’06 Proceedings of the 29th annual international
ACM SIGIR. 2006
\bibitem{amazon-item2item} Linden, G. Amazon.com recommendations: item-to-item
collaborative filtering [Текст]  / G. Linden, B. Smith, J. York// Internet Computing 7:1. 2003. с. 76---80


\bibitem{amazon-linden} Linden, G.D. Collaborative Recommendations Using
Item-to-Item Similarity Mapping / G. D. Linden, J. A. Jacobi, E. A. Benson
// US Patent 6,266,649 (to Amazon.com), Patent
and Trademark Office, Washington, D.C. Т. 2001
\bibitem{imdb} IMDB [Электронный ресурс]. --- Режим доступа: http://www.imdb.com/
\bibitem{lastfm} LastFm [Электронный ресурс]. --- Режим доступа: http://www.last.fm/ru/
\bibitem{amazon} Amazon [Электронный ресурс]. --- Режим доступа: https://www.amazon.com/gp/gw/ajax/s.html/
\bibitem{fdca} Ким, О. Дж. Факторный, дискриминантный и кластерный анализ [Текст] / О. Дж. Ким,
 Ч.У. Мьюллер,  У.Р. Клекка[и др.]. Финансы и статистика, 1998. с. 216.
\bibitem{ir1} Manning, C. D. An Introduction to Information Retrieval / C. D. Manning, P. Raghavan, H. Schütze. // New York, NY, USA: Cambridge University Press, 2008.
\bibitem{ir2} Rosel M. Introduction to Information Retrieval and Text Clustering [Текст] / M. Rosel // KTH CSC,
2006.
\bibitem{ir3} Hiemstra D. Information Retrieval Models. Ayse Goker and John Davies (eds.) [Текст]  / D. Hiemstra //
Information Retrieval: Searching in the 21st Century, 2009.
\bibitem{ir4} Salton G. Automatic Text Processing: The Transformation, Analysis, and
Retrieval of Information by Computer [Текст]  /G. Salton // Addison Wesley, 1989.
\bibitem{jester} Goldberg, K. Eigentaste: A constant time collaborative filtering algorithm [Текст]  / K. Goldberg,
T. Roeder, D. Gupta [и др.] // Information Retrieval. 2001. Т. 4. С. 133---151.
\bibitem{norm} Jin, R. A study of methods for normalizing user ratings
in collaborative filtering [Текст]  / R. Jin, L. Si. Carnegie // Proc. SIGIR ’04 Proceedings of the 27th annual
international ACM SIGIR conference on Research and development in
information retrieval. 2004. С. 568---569.
\bibitem{sparse1} Papagelis, M. Alleviating the Sparsity Problem of
Collaborative Filtering Using Trust Inferences [Текст]  / M. Papagelis, D. Plexousakis, T. Kutsuras
// iTrust’05 Proceedings of the
Third international conference on Trust Management. 2005. С. 224---239.
\bibitem{sparse2} Liu, Z. Sparse Matrix Prediction Filling in Collaborative Filtering [Текст] / Z. Liu, H. Wang,
W. Qu [и др.] // International Conference on Scalable Computing and
Communications. 2009.

\bibitem{sparse3} Brain, J. P. Isolating Matrix Sparsity in Collaborative Filtering Ratings
Matrices [Текст]  /J. P. Brian, Eun-Joo L // Proceedings of the International Conference on Data Mining. 2013.
\bibitem{social_osipov} Осипов, Г. В. / Осипов Г.В., Москвичев Л.Н. // Социология. Основы общей теории. М.: Норма, 2003.
\bibitem{vsm1} Musto, C. Enhanced Vector Space Models for Content-based Recommender
Systems [Текст]  / C. Musto // RecSys '10 Proceedings of the fourth ACM conference on Recommender systems. 2010,
C. 361-364
\bibitem{8020-1} Pan, R. One-Class Collaborative Filtering [Текст]  /R. Pan, Y. Zhou, B. Cao // Data Mining, ICDM
’08. 2008.
\bibitem{8020-2} Sarwar, B.M. Recommender systems for large-scale e-commerce:
Scalable neighborhood formation using clustering [Текст]   /
B. M. Sarwar, G. Karypis, J. Konstan // Proceedings of
the fifth international conference on computer and information technology. 2007.
\bibitem{rs-eval-shani} Shani, G. Evaluating Recommender Systems [Электронный ресурс]. --- Режим доступа: http://www.bgu.ac.il/~shanigu/Publications/EvaluationMetrics.17.pdf / G. Shani, A. Gunawardana //
2009.
\bibitem{herloker-eval} Herlocker, J. Evaluating Collaborative Filtering Recommender Systems [Текст]  / J. Herlocker // ACM
TRANSACTIONS ON INFORMATION SYSTEMS. 2004. Т. 22. С. 5---53.
\bibitem{eval-precision} Najafi, S. Evaluating Prediction Accuracy for Collaborative Filtering
Algorithms in Recommender Systems [Текст]  / S. Najafi, Z. Salam // DEGREE PROJECT TECHNOLOGY.
2016.
\bibitem{cluster2} Ester, M. A density-based algorithm for discovering clusters in large spatial databases with
noise [Текст]  / M. Ester, H.-P. Kriegel, J. Sander [и др.] // Proceedings of the International
Conference on Knowledge Discovery and Data Mining (KDD ’96). 1996.

\bibitem{cluster3} Ankerst, M. OPTICS: ordering points to identify the clustering structure [Текст]  / M. Ankerst,
M. M. Breunig, H.-P. Kriegel [и др.] // Proceedings of ACM SIGMOD
Conference. 1999. с. 49---60.
\bibitem{cluster4} Zhang, T. BIRCH: an efficient data clustering
method for very large databases [Текст]  /T. Zhang, R. Ramakrishnan, M. Livny  // Proceedings of the ACM SIGMOD
International Conference on Management of Data. 1996. Т. 25. с. 103---114.
\bibitem{cluster5} Su, X. Query size estimation using clustering techniques [Текст]  / X. Su, M. Kubat, M. A. Tapia
[и др.] // Proceedings of the 17th International Conference on Tools with Artificial
Intelligence (ICTAI ’05). 2005. с. 185---189.




\bibitem{cluster6} Li, Q. Clustering Approach for Hybrid Recommender System [Текст]  / Q. Li, B. Kim // WI
’03 Proceedings of the 2003 IEEE/WIC International Conference on Web
Intelligence. 2003.
\bibitem{cluster7} Karlgren, J. Newsgroup clustering based on user behavior --- a recommendation
algebra [Электронный ресурс]. ---  http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.47.9381\&rep=rep1\&type=pdf / J. Karlgren // 1994.
\bibitem{cluster8} Gong, S. A. Collaborative Filtering Recommendation Algorithm Based on User
Clustering and Item Clustering [Текст]  / S. A. Gong // JOURNAL OF SOFTWARE,. 2010. Т. 5.
\bibitem{stat1} Su, X. Collaborative filtering for multi-class data using belief
nets algorithms [Текст]  / X. Su, T. M. Khoshgoftaar // Proceedings of the International Conference on Tools with
Artificial Intelligence (ICTAI ’06). 2006. с. 497---504.
\bibitem{stat2} Hofmann, T. Probabilistic latent semantic indexing [Текст]  / T. Hofmann // ACM SIGIR ’99. 1999.
с. 50---57.
\bibitem{stat3} Jin, X. Web usage mining based on probabilistic latent
semantic analysis  [Текст] / X. Jin, Y. Zhou, B. Mobasher. // ACM KDD ’04. 2004. с. 197---205.
\bibitem{stat4} Popescul, A. Probabilistic models for unified collaborative and content-based recommendation
in sparse-data environments [Текст]  / A. Popescul, L. Ungar, D. Pennock [и др.] // UAI
’01 Proceedings of the 17th Conference in Uncertainty in Artificial Intelligence.
2001. с. 437---444.
\bibitem{stat5} Landauer T., Littman M., (Bellcore) Bell Communications Research.
Computerized cross-language document retrieval using latent semantic indexing
[Электронный ресурс]. ---  https://patents.google.com/patent/US5301109A/en // 1994
\bibitem{stat6} Deerwester, S. Indexing by latent semantic analysis [Текст]  / S. Deerwester, S. Dumais, G. W. Furnas
[и др.] // Journal of the American Society for Information Science. 1990. Т. 41.
с. 391---407.
\bibitem{stat7} Hofmann, T. Latent class models for collaborative filtering [Текст]  / T. Hofmann, J. Puzicha //
Proceedings of the 16th International Joint Conference on Artificial Intelligence
(IJCAI ’99). 1999. с. 688---693.
\bibitem{stat8} Hofmann, T. Unsupervised learning by probabilistic latent semantic analysis [Текст]  / T. Hofmann //
Machine Learning. 2001. Т. 42. с. 177---196.121
\bibitem{stat10} Hofmann, T. Latent Semantic Models for Collaborative Filtering [Текст]  / T. Hofmann // ACM Trans.
Information Systems. 2004. Т. 22. С. 89---115.
\bibitem{stat11} Howard, R. A. Dynamic Programming and Markov Processes [Текст] / R. A. Howard // MIT Press,
Cambridge, Mass, USA. 1960.
\bibitem{stat12} Kearns, M. A sparse sampling algorithm for near-optimal
planning in large Markov decision processes [Текст]  / M. Kearn, Y. Mansour, A. Y. Ng
// Machine Learning. 2002. Т. 49. С. 193---208.
\bibitem{learning4} Billsus, D. Learning Collaborative Information Filters  [Текст] / D. Billsus, M. Pazzan // Int’l Conf.
Machine Learning. 1998.
\bibitem{learning1} Miyahara, K. Collaborative filtering with the simple Bayesian
classifier  [Текст] / K. Miyahara, M. J. Pazzani // Proceedings of the 6th Pacific Rim International Conference on
Artificial Intelligence. 2000. с. 679---689.
\bibitem{learning2} Cohn, D. Improving Generalization with Active Learning  [Текст] 
/ D. Cohn, L. Atlas, R. Ladner //
Machine Learning. 1994. Т. 15. С. 201---221.
\bibitem{learning3} Cohn, D. Active Learning with Statistical Models
 [Текст] / D. Cohn, Z. Ghahramani, M. Jordan //
Artificial Intelligence Research. 1996. Т. 4. С. 129---145.

\bibitem{learning5} Fawcett, T. Combining Data Mining and Machine Learning for
Efficient User Profiling  [Текст] / T. Fawcett, F. Provost // Second Int’l Conf. Knowledge Discovery and Data
Mining (KDD-96). 1996.

\bibitem{learning6} Freund, Y. Selective Sampling Using the Query by Committee Algorithm  [Текст] / Y. Freund,
H.S. Seung, E. Shamir [и др.] // Machine Learning. 1997. Т. 28. С. 133---168.

\bibitem{learning7} Pazzani, M. Learning and Revising User Profiles: The Identification of
Interesting Web Sites  [Текст] / M. Pazzani, D. Billsus // Machine Learning. 1997. С. 313---331.
\bibitem{learning8} Lang, K. Newsweeder: Learning to Filter Netnews  [Текст] / K.Lang // Proc. 12th Int’l Conf.
Machine Learning. 1995.
\bibitem{learning9} Lee, W.S. Collaborative Learning for Recommender Systems  [Текст] / W. S. Lee // Int’l Conf.
Machine Learning. 2001.
\bibitem{learning10} Lewis, D. Heterogeneous Uncertainty Sampling for Supervised
Learning  [Текст] /  D. Lewis, J. Catlett // 11th Int’l Conf. Machine Learning. 1994. С. 148---156.122
\bibitem{learning11} Goldman, S. A., Warmuth M. K. Learning binary relations using weighted majority
voting  [Текст] / S. A. Goldman // Machine Learning. 1995. Т. 20. с. 245---271.
\bibitem{learning12} Balabanovi, M. Exploring versus exploiting when learning user models for text
recommendation  [Текст] / M. Balabanovi // User Modelling and User-Adapted Interaction. 1998. Т. 8.
с. 71---102.
\bibitem{content1} Pazzani, M. J. A framework for collaborative, content-based and demographic
filtering  [Текст] / M. J. Pazzani // Artificial Intelligence Review. 1999. с. 393---40.
\bibitem{content3} Popescul, L. H. Probabilistic models for unified collaborative and content-based recommendation
in sparse-data environments  [Текст] / L. H. Popescul, D. M. Pennock [и др.] //
Proceedings of the 17th Conference in Uncertainty in Artificial Intelligence (UAI
’01). 2001. с. 437---444.
\bibitem{content4} Soboroff, I. Combining Content and Collaboration in Text Filtering [Текст] / I. Soboroff, C. Nicholas //
Int’l Joint Conf. Artificial Intelligence Workshop: Machine Learning for
Information Filtering. 1999.
\bibitem{content6} Hirsh, H. Recommendation as Classification: Using Social
and Content-Based Information in Recommendation  [Текст] / C. Basu, H. Hirsh, W. Cohen // Recommender Systems.
Papers from 1998 Workshop, Technical Report WS-98-08, AAAI Press 1998.
1998.



\bibitem{content7} Claypool, M. Combining Content-Based and Collaborative Filters in an Online Newspaper  [Текст] /
M. Claypool, A. Gokhale, T. Miranda [и др.] // Proc. ACM SIGIR ’99 Workshop
Recommender Systems: Algorithms and Evaluation. 1999.
\bibitem{content9} Melville, P. Content-Boosted Collaborative Filtering
for Improved Recommendations
 [Текст] / P. Melville, R. J. Mooney, R. Nagarajan
// Proc. 18th Nat’l Conf. Artificial Intelligence. 2002.
\bibitem{content10} Balabanovi M., Shoham Y. Fab: Content-based, collaborative recommendation  [Текст] / M. Balabanovi, Y. Shoham //
Communications of the ACM. 1997. Т. 40. с. 66---72.
\bibitem{content11} J. Mooney. Content-based book recommendation using learning for
text categorization  [Текст] / J. Mooney, L. Roy // Proceedings of the Workshop on Recommender Systems:
Algorithms and Evaluation. 1999.123
\bibitem{content12}  Pasquale, L. Chapter 3
Content-based Recommender Systems: State of the Art and Trends  [Электронный ресурс]. ---  http://facweb.cs.depaul.edu/mobasher/classes/ect584/papers/contentbasedrs.pdf/
L. Pasquale, M. Gemmis, G. Semeraro [и др.].
\bibitem{empirical-cf} Breese, J. S. Empirical analysis of predictive algorithms
for collaborative filtering  [Текст] / J. S. Breese., D. Heckerman, C. Kadie // Proc. of UAI. 1998.



\bibitem{coscial-rec-survey} Su, X. A survey of collaborative filtering based social
recommender systems  [Текст] / X. Su, T. Khoshgoftaar // Computer Communications. 2014. Т. 41. С. 1---10.
\bibitem{surveyCf} Su X., Khoshgoftaar T. A survey of collaborative filtering techniques // Advances
in Artificial Intelligence. 2009. с. 19.
\bibitem{Marlin04collaborativefiltering} Marlin B. Collaborative Filtering: A Machine Learning Perspective  [Электронный ресурс]. ---
https://pdfs.semanticscholar.org/5d89/3123b58a754ecb06334a97f151f698cf24dd.pdf / B. Marlin // 2004.
\bibitem{temporal-model} Campos Soto, P. G. Temporal Models in Recommender Systems:An Exploratory
Study on Different Evaluation Dimensions  [Электронный ресурс]. ---
http://ir.ii.uam.es/reshet/pub/uam11.pdf / P. G. Campos Soto // 2011

\bibitem{bayesian-model} Guo, S. Bayesian Recommender Systems: Models and Algorithms  [Электронный ресурс]. ---
http://users.cecs.anu.edu.au/~sguo/thesis.pdf/ S. Guo // 2011

\bibitem{most-popular} Yao, W. CCCF: Improving Collaborative Filtering via Scalable User-Item Co-Clustering  [Текст] /
W. Yao, L. Xudong, X. Min [и др.] // WSDM ’16 Proceedings of the Ninth ACM
International Conference on Web Search and Data Mining. 2016. С. 73---82.

\bibitem{most-success} Hu, R. Using personality information in collaborative filtering for new
users [Текст]  / R. Hu, P. Pu. // Recommender Systems and the Social Web. 2010.

\bibitem{person-rec-item-based} Mayuri, P. A Personalized Recommendation on the
Basis of Item Based Algorithm [Текст]  / P. Mayuri, P. Sonal, G. Dhanokar // International Journal of Computer Science and
Information Technologies. 2015. Т. 6. С. 4309---4312.

\bibitem{disser0} Li, L. Next Generation of Recommender Systems: Algorithms and Applications   [Электронный ресурс]. ---
https://digitalcommons.fiu.edu/cgi/viewcontent.cgi?referer=https://www.google.com/\&httpsredir=1\&article=2550\&context=etd / L. Li // 2014

\bibitem{melville} Melville, P. Recommender Systems [Текст]  / P. Melville, V. Sindhwani // Encyclopedia of
Machine Learning. 2010. С. 829---838

\bibitem{grouplens} Resnick, P. GroupLens:an open architecture for collaborative filtering of netnews [Текст]  / P. Resnick,
N. Iacovou, M. Suchak [и др.] // ACM CSCW. 1994. Т. 40. С. 175---186

\bibitem{bellcore} Hill, W. Recommending and evaluating choices in a virtual community of use [Текст]  / W. Hill,
L. Stead, M. Rosenstein [и др.] // ACM CHI. 1995. с. 194---201.

\bibitem{neighbor-cf} Knees, P. Improving Neighborhood-Based Collaborative
Filtering by Reducing Hubness [Текст]  / P. Knees, A. Flexer, D. Schnitzer // ICMR 14 Proceedings of International
Conference on Multimedia Retrieval. 2014.

\bibitem{threshold1} Aggarwal, C. C. Recommender Systems [Текст]  / C. C. Aggarwal // Springer, 2016. с. 498.

\bibitem{threshold2} Bøe, C. Collaborative filtering for recommending movies [Текст]  / C. Bøe // Master’s thesis,
Norwegian University of Science and Technology. 2007. Т. 40. С. 56---58.

\bibitem{threshold3} Jojic, O. A probabilistic definition of item similarity
	[Текст]
/ O. Jojic, M. Shukla, N. Bhosarekar //
Proceedings of the fifth ACM conference on Recommender systems. 2011. Т. 40.
с. 229---236.

\bibitem{threshold4} Cleger-Tamayo, S. A new criteria for selecting
neighborhood in memory-based recommender systems [Текст]  / S. Cleger-Tamayo, J. M. Fernandez-Luna,
J. F. Huete // Proceedings of the 14th
international conference on Advances in artificial intelligence: spanish association
for artificial intelligence. 2011. с. 423---432.

\bibitem{threshold5} Ma, H. Learning to recommend [Текст]  / H. Ma // The Chinese University of Hong Kong, 2009.

\bibitem{ub-assumption} Lam, C. P. Collaborative filtering using associative neural memory [Текст]  / C. P. Lam // ITWP’03
Proceedings of the 2003 international conference on Intelligent. 2003. С. 153---
168.

\bibitem{user-item-cf} Yao, G. User-Based and Item-Based Collaborative Filtering
Recommendation Algorithms Design [Электронный ресурс]. --- https://www.semanticscholar.org/paper/User-Based-and-Item-Based-Collaborative-Filtering-Yao-Cai/c4b2363ba7c15c67a2c6b2d079e325f1a33d6b75 / G. Yao, L. Cai // 2015

\bibitem{rs-cf} Zhang, Y. A Research of Job Recommendation System Based on
Collaborative Filtering [Текст]  / Y. Zhang, C. Yang, Z. Niu // Computational Intelligence and Design (ISCID). 2015.

\bibitem{ringo} Shardanand, U. Social information filtering: Algorithms for automating
<<word of mouth>> [Текст]  / U. Shardanand, P. Maes // ACM CHI. 1995. С. 210---217.

\bibitem{pearson-trans} Sotos, A. The non-transitivity of Pearson’s correlation coefficient: an educational
perspective [Текст]  / A. Sotos, S. Vanhoof, W. Van den Noortgate [и др.] // Proceedings
of the 56th Session of the ISI. С. 4609---4613.

\bibitem{google-news} Google News [Электронный ресурс]. --- https://news.google.ru/

\bibitem{changes} Koren, Y. Collaborative Filtering with Temporal Dynamics [Текст]  / Y. Koren // Proceedings of the
15th ACM SIGKDD international conference on Knowledge discovery and data
mining. 2009. С. 447---456.

\bibitem{psy} Посыпанова, О. Экономическая психология: психологические аспекты
поведения потребителей [Текст]  / О. Посыпанова // КГУ им. К.Э. Циолковского, 2012.

\bibitem{hetero-spotify} Recommending music on Spotify with deep learning [Электронный ресурс]. ---  http://benanne.
github.io/2014/08/05/spotify-cnns.html // 2014
2017-09-15.

\bibitem{hetero1} Solomon J. Heterogeneity in Customization of Recommender Systems By Users
with Homogenous Preferences [Текст]  / J. Solomon // Proceedings of the CHI ’16 Proceedings of the
2016 CHI Conference on Human Factors in Computing Systems. 2016. С. 4166---
4170.

\bibitem{fuzzy-ponomarev} Пономарев, А. С. Нечеткие множества в задачах автоматизированного
управления и принятия решений [Текст]  / А. С. Пономарев //  НТУ ХПИ, 2005.

\bibitem{expert-systems} Джексон, П. Введение в экспертные системы [Текст]   / П. Джексон // Вильямс, 2001. с. 624.

\bibitem{set-theory} Верещагин, Н. К. Лекции по математической логике и теории алго-
ритмов.Часть 1. Начала теории множеств [Текст]  /Н. К. Верещагин, А. Шень // 4-е изд. М: МЦНМО, 2012. с. 112
с.

\bibitem{matan} Зорич, В. А. Математический анализ. В 2-х ч.[Текст]   /  В.А. Зорич // М.: ФАЗИС; Наука,
1984. с. 640.
\bibitem{citation} Liu, H. Context-Based Collaborative Filtering for Citation
Recommendation [Электронный ресурс]. ---  https://ieeexplore.ieee.org/document/7279056
/ H. Liu, X. Kong, X. Bai // 2015.

\bibitem{bank} Ляпина, Е. Р. Проектирование банковского рекомендательного сервиса с
использованием методов машинного обучения [Электронный ресурс]. ---
https://www.hse.ru/edu/vkr/182625301/ Е. Р. Ляпина // 2016.

\bibitem{ml-data} MovieLens Data [Электронный ресурс]. ---
https://grouplens.org/datasets/movielens/.

\end{thebibliography}
